title TBD

### 2016-01-11 SC-challenge.tex
small changes

\acmformat{Kyle E. Niemeyer, Arfon M.\ Smith, and Daniel M.\ Katz, 2016. Title TBD.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

@@

Author's addresses: K. E. Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University; 
A. M. Smith,
GitHub, Inc.; 
D. M. Katz,
Computation Institute, University of Chicago \& Argonne National Laboratory.
\end{bottomstuff}

>>>>

\acmformat{Kyle E. Niemeyer, Arfon M.\ Smith, and Daniel S.\ Katz, 2016. Title TBD.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

@@

Some work by D. S. Katz was supported by the National Science Foundation (NSF) while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.

Author's addresses: K. E. Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University; 
A. M. Smith,
GitHub, Inc.; 
D. S. Katz,
Computation Institute, University of Chicago \& Argonne National Laboratory.
\end{bottomstuff}
